Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-16 ms.tex
Continue adjusting linear algebra math in main text

A simultaneous beamforming filling the entire field of view can also be achieved by a two-dimensional spatial Fast Fourier Transform (FFT) of the measurements on the aperture plane. This can be enabled even for an irregular layout of station elements by gridding the calibrated electric fields measured by the station elements. The Optimal Map Making formalism \citep[OMM;][]{Tegmark1997a} formalism adopted by \citet{Morales2011} is the basis of the architecture called E-field Parallel Imaging Correlator \cite[EPIC;][]{Thyagarajan+2017},
\begin{align}
    \widetilde{\mathcal{E}}_m^\alpha(\hat{\boldsymbol{s}}_k) &= \sum_j \delta^2 \boldsymbol{r}_j \, e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j} \left(\sum_{a_m} \sum_p \widetilde{W}_{a_m}^{p\alpha*}(\boldsymbol{r}_j-\boldsymbol{r}_{a_m}) \, \widetilde{E}_{a_m}^p \right) \, , \label{eqn:intra-station-pol-hol-img-epic}
\end{align}
whose equivalent linear algebraic representation is 
\begin{align}
  \widetilde{\boldsymbol{\mathcal{E}}}_{[m,\alpha,\hat{\boldsymbol{s}}]} &= \mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\,\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\,\widetilde{\mathbf{E}}_{[p,\boldsymbol{r}_{a_m}]} \, . \label{eqn:intra-station-pol-hol-img-epic-LA}
\end{align}
The subscripted variables on either side of $\leftarrow$ indicate the transformation carried out by the associated matrix. For example, $\mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\coloneqq e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j}$ denotes the Hermitian of the Fourier matrix (inverse Fourier matrix) transforming variables defined on aperture grid, $\boldsymbol{r}_j$, to sky grid, $\hat{\boldsymbol{s}}_k$. And, $\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\coloneqq \{\widetilde{W}_{a}^{\alpha p *}(\boldsymbol{r}_j-\boldsymbol{r}_a)\}$ is a matrix, where each column corresponds to the gridding weights of an element, $\widetilde{W}_{a}^{p\alpha}(\boldsymbol{r}_j)$, and the rows correspond to the aperture grid locations, $\boldsymbol{r}_j$. In each column, the holographic weights are shifted to the element location, $\boldsymbol{r}_{a}$.
% And, $\mathbf{W}_{[p,\boldsymbol{r}_{a}\leftarrow \alpha,\boldsymbol{r}]}\coloneqq \{W_{a}^{p\alpha}(\boldsymbol{r}_{a}-\boldsymbol{r}_j)\}$ is a matrix, where each row corresponds to the holographic pattern of an element, $W_{a}^{p\alpha}(\boldsymbol{r}_j)$, and the columns correspond to the aperture grid locations, $\boldsymbol{r}_j$. In each row, the holographic weights are shifted to the element location, $\boldsymbol{r}_{a}$.

>>>>

A simultaneous beamforming filling the entire field of view can also be achieved by a two-dimensional spatial Fast Fourier Transform (FFT) of the measurements on the aperture plane. This can be enabled even for an irregular layout of station elements by gridding the calibrated electric fields measured by the station elements. The Optimal Map Making formalism \citep[OMM;][]{Tegmark1997a} formalism adopted by \citet{Morales2011} is the basis of the architecture called E-field Parallel Imaging Correlator \cite[EPIC;][]{Thyagarajan+2017},
\begin{align}
    \widetilde{\mathcal{E}}_m^\alpha(\hat{\boldsymbol{s}}_k) &= \sum_j \delta^2 \boldsymbol{r}_j \, e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j} \left(\sum_{a_m} \sum_p \widetilde{W}_{a_m}^{\alpha p*}(\boldsymbol{r}_j-\boldsymbol{r}_{a_m}) \, \widetilde{E}_{a_m}^p \right) \, , \label{eqn:intra-station-pol-hol-img-epic}
\end{align}
whose equivalent linear algebraic representation is 
\begin{align}
  \widetilde{\boldsymbol{\mathcal{E}}}_{[m,\alpha,\hat{\boldsymbol{s}}]} &= \mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\,\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\,\widetilde{\mathbf{E}}_{[p,\boldsymbol{r}_{a_m}]} \, . \label{eqn:intra-station-pol-hol-img-epic-LA}
\end{align}
The subscripted variables on either side of $\leftarrow$ indicate the transformation carried out by the associated matrix. For example, $\mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\coloneqq e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j}$ denotes the Hermitian of the Fourier matrix (inverse Fourier matrix) transforming variables defined on aperture grid, $\boldsymbol{r}_j$, to sky grid, $\hat{\boldsymbol{s}}_k$. $\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\coloneqq \{\widetilde{W}_{a}^{\alpha p *}(\boldsymbol{r}_j-\boldsymbol{r}_a)\}$ is a matrix, where each column corresponds to the gridding weights of an element, $\widetilde{W}_{a}^{\alpha p*}(\boldsymbol{r}_j)$, and the rows correspond to the aperture grid locations, $\boldsymbol{r}_j$. In each column, the gridding weights are shifted to the element location, $\boldsymbol{r}_{a}$. 
% And, $\mathbf{W}_{[p,\boldsymbol{r}_{a}\leftarrow \alpha,\boldsymbol{r}]}\coloneqq \{W_{a}^{p\alpha}(\boldsymbol{r}_{a}-\boldsymbol{r}_j)\}$ is a matrix, where each row corresponds to the holographic pattern of an element, $W_{a}^{p\alpha}(\boldsymbol{r}_j)$, and the columns correspond to the aperture grid locations, $\boldsymbol{r}_j$. In each row, the holographic weights are shifted to the element location, $\boldsymbol{r}_{a}$.
